Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-22 ms.tex
Franks comments addressed except for chi^2 question.

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We constrain the newly-introduced decorated Halo Occupation Distribution (HOD) 
  model using SDSS DR7 measurements of projected galaxy clustering, $\wprp (r_{\rm p})$ 
  of galaxies in r-band luminosity-threshold samples. 
  The decorated HOD is a model for the galaxy--halo
  connection that augments the traditional HOD by allowing for the possibility of 
  {\em galaxy assembly bias}: galaxy luminosity may be correlated with dark matter halo
  properties besides mass, $\mvir$. We demonstrate that it
  is not possible to rule out galaxy assembly bias using DR7 measurements of galaxy 
  clustering alone. Moreover, galaxy samples $\magr<-20, -20.5$
  favor strong levels of central galaxy assembly bias. These samples prefer scenarios  
  in which high-concentration halos are more likely to host a central galaxy
  relative to low-concentration halos of the same $\mvir.$ We rule out
  zero assembly bias with high significance for these
  samples. Satellite galaxy assembly bias is significant for the
  faintest sample we study, $\magr<-19.$ We find no evidence for
  assembly bias in the $\magr<-21$ sample. Assembly bias should be accounted for 
  in galaxy clustering analyses or attempts to exploit galaxy clustering to constrain cosmology. 
  In addition to presenting the first constraints on HOD models that accommodate assembly bias, our analysis 
  includes numerous improvements over previous analyses of this data set and 
  supersedes previously published results, even in the case of a standard HOD analysis.
\end{abstract}

@@

In much of the literature on this topic,
the character of the supporting evidence
suffers from a severe shortcoming.
Until very recently, the only models that have been fit to
observational clustering measurements have been traditional models
in which assembly bias is assumed from the outset to be zero.
Models that include assembly bias such as semi-analytic models
are typically too computationally expensive to compare to data in a manner 
that enables statistical constraints on model parameters. Such models are usually 
compared to data on a case-by-case basis \citep[e.g.,][]{croton_etal07}, prohibiting
any conclusive statement to be made about the strength of any assembly bias signal.

@@

We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter
halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} 
and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}. In particular, we use the {\tt halotools\_alpha\_version2} 
version of the $z=0$ snapshot
of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are based on the virial radius
density contrast given in \citet{bryan_norman98}. When populating this catalog with mock galaxies, we only use
present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles. The minimum 
peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^{10}\, h^{-1}\mathrm{M}_{\odot}$ 
and this prevents us from analyzing samples with $M_r > -19$.

@@

The five parameters of HOD models that are varied in standard analyses are $\log (M_{\rm min})$,
$\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$, though, as we show below, central galaxies usually
outnumber satellite galaxies by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually
vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are
many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\vert \mvir \rangle$ and
$\langle N_{\rm sat}\vert \mvir \rangle$. We have made choices that mimic the standard SDSS DR7 analysis of
\citet{zehavi_etal11}, to expedite comparisons with their results. However, our choice does deviate from 
the choice of \citet{zehavi_etal11} in one respect. The mean satellite occupation of \citet{zehavi_etal11} 
is that of Eq.~(\ref{eq:nsat}) multiplied by an overall factor of $\langle N_{\rm cen} \vert \mvir \rangle$. 
We have chosen not to use this as our default because it can introduce difficulties in some analyses 
\citep[see the discussion of blue galaxy samples in][]{zentner_etal14} and because, as we have verified 
explicitly, the extra factor introduces only small quantitative changes to our results and no qualitative 
changes.

@@

After populating a halo catalog with mock galaxies, we calculate the
comoving number density of our mock galaxy sample as $n_{\rm g} =
N_{\rm gal} / L_{\rm box}^3$, where $N_{\rm gal}$ is the total number of
galaxies in the mock sample. We apply the distant-observer
approximation and use the simulation z-axis as the line-of-sight
direction, and the distance between points in the $xy$-plane to define
the projected distance $\rp.$ We place mock galaxies into
redshift-space by replacing each galaxy's $z$-coordinate with
$z_{\rm RS} = z + V_{\rm z}/H_0.$ We count pairs of points in each of
our $\rp$ bins, rejecting pairs with line-of-sight distances in redshift space, $\Delta z_{\rm RS}$, 
exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
depth chosen by \citet{zehavi_etal11}, both in their analysis of the SDSS
DR7 data and in their modeling. Finally, having populated mocks, 
we perform the computation of the projected two-point galaxy correlation 
function, $w_{\rm p}(r_{\rm p})$ using the publicly-available {\tt CorrFunc} 
package \citep{corrfunc} which has been extensively optimized for computational speed.

@@

%=-------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=8.0cm]{central_hod_comparison.pdf}
\includegraphics[width=8.5cm]{satellite_hod_comparison.pdf}
\caption{
We show the first moments of the central and satellite occupation distributions
from the best-fit models to the $\magr<-20$ sample in the left and right
panels, respectively. The solid, purple curve shows the HOD of our best-fit model
that includes the effect of assembly bias; the solid, orange curve shows the HOD
of the best-fit model in which assembly bias is assumed to be zero;
the dashed, black curve shows the best-fit HODs from \citet{zehavi_etal11}.
The light purple error band around the decorated HOD results contains 68\% of 
all samples of the posterior within $\Delta \chi^2 \le 5.89$ of the best-fit model at 
each bin of halo mass. For any individual model, 
the values of the HOD at each mass point are obviously correlated and do 
not vary independently from one mass bin to another. 
}
\label{fig:directhodcomparison}
\end{center}
\end{figure*}
%----------------------------------------------------------------------------------------------------

@@

Though the evidence for assembly bias is the most significant for the $M_r<-20$ sample,
there are hints of galaxy assembly bias in other samples. Satellite galaxies show a marginal preference
for occupying halos of higher concentration in the $M_r < -19$ threshold sample, with $A_{\rm sat}>0$ at 
85\%. The $M_r < -19.5$ sample exhibits weak preference for a positive correlation of galaxy occupation 
with halo concentration at fixed mass for both satellite galaxies and central galaxies. The low value of 
$\chi^2$ in this case is also suggestive of possible over-fitting using these additional parameters (but see 
the discussion in the subsequent paragraph). Continuing upward with luminosity,
the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias, 
with $A_{\rm cen}>0$ at 92.3\%. Lastly, there is no preference for either central galaxy or 
satellite galaxy assembly bias for the $M_r < -21$ threshold sample, 
for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
are consistent with zero well within 1$\sigma$. The implications of all of these results, particularly for 
quantities derived from HODs, are far too numerous 
to address in the present manuscript; however, we plan to address them in forthcoming publications.

@@

Another possible explanation for having more luminous galaxies reside
in higher concentration halos is halo-halo interactions.  Recent work
on halo evolution suggests that a more physical definition of the size
of a halo should be $\sim 2-3$ times the traditional virial radius
\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,more_etal15,sunayama_etal16}.
This ``splashback radius" incorporates ``splashback" halos that have
passed within the dense environment of the central halo, but are
traditionally classified as distinct halos despite being strongly
influenced by the environment of the central
halo. \citet{wang_etal09}, \citet{wetzel_etal14},
\citet{sunayama_etal16}, all find that these ``splashback" halos are a
significant cause of halo assembly bias on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, where assembly bias is most pronounced and
strongly scale dependent. Consequently, decorated HOD models exhibit
this same feature \citep{hearin_etal16}, and is not a coincidence that
the greatest improvement of the decorated HOD in the description of
galaxy clustering occurs on these same length scales (see
Fig.~\ref{fig:Mr19samples}-\ref{fig:Mr21samples} and the associated
discussion).

This ``splashback" hypothesis has further merit in that it has the
same sense as suggested by the data. Splashback halos have experienced
mass loss as a consequence of their tidal interactions with a larger,
nearby halo. As a consequence, splashback halos are expected to be
less massive than `regular' host halos that host similar galaxies
\citep{dalal_etal08}.  Meanwhile, high concentrations due to tidal
truncation are a hallmark of splashback halos
\citep{sunayama_etal16}.  The implication is
a population of halos, correlated on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, that have concentrations that are high for their
mass and galaxies that are overluminous for their mass. This is
precisely the sense of assembly bias suggested by our analysis.  Note,
though, that this splashback effect cannot explain galaxy assembly
bias on large, linear scales.

@@

We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,
$\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}.
The novelty of our work is that we have performed these analyses using the
decorated Halo Occupation Distribution (HOD) formalism, which allows for galaxy
assembly bias and was introduced by \citet{hearin_etal16} precisely for this purpose.
In this work, we provide the first quantitative constraints on
assembly bias derived from the Decorated HOD. Projected galaxy clustering, 
$\wprp(r_{\rm p})$ is already very well-measured within SDSS DR7, therefore it is likely 
that further improvements on assembly bias constraints at low-redshift will require the use of additional 
observables such as galaxy--galaxy lensing, group statistics, void statistics, or numerous other possibilities. 
We are currently exploring many of those possibilities and will report on those results in a forthcoming publication.

Our most important conclusions are as follows.
%
\ben
%
\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
%
\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we study. Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias. The $\magr<-19$ sample favors satellite assembly bias. Assembly bias in these samples improves the capability of the model to describe galaxy clustering near
the one-halo to two-halo transition at $r_{\rm p} \sim 2 \, h^{-1}\mathrm{Mpc}$.
%
\item The evidence for galaxy assembly bias weakens for brighter galaxy samples: Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cens}=0$ and $A_{\rm sats}=0.$ This is consistent with the well-established result that
{\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples
\citep[see, e.g., Figure 8 of][and references therein]{hearin_etal16}.
%
\item Our posteriors and best-fit parameters summarized in
Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11},
as direct-mock-population together with the Decorated HOD allows us to account for
highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data.
We note that our findings update the original \citet{zehavi_etal11} results
{\em even for our fits to standard HODs without assembly bias}, because
the original results were derived from MCMC chains that did not sufficiently sample the HOD model posteriors.
%
\een
%

@@

We thank Zheng Zheng for his help in diagnosing the
differences between the present analysis and the SDSS DR7
analysis presented in \citet{zehavi_etal11}. We thank Manodeep 
Sinha for help installing and running the {\tt CorrFunc} package 
as well as comments on an earlier draft of this manuscript. ARZ and 
APH are grateful to Prince Rogers Nelson for inspiring our creativity. 
The authors gratefully acknowledge the Gauss Centre for Supercomputing
e.V. (www.gauss-centre.eu) and the Partnership for Advanced
Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the
MultiDark simulation project by providing computing time on the GCS
Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ,
www.lrz.de). The Bolshoi simulations have been performed within the
Bolshoi project of the University of California High-Performance
AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
Research Center. The work of ARZ was supported by the US National Science
Foundation via grant AST 1517563. FvdB is supported by the US National Science
Foundation through grant AST 1516962. APH is funded through the Yale Center 
for Astronomy \& Astrophysics Prize fellowship.

>>>>

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We constrain the newly-introduced decorated Halo Occupation Distribution (HOD) 
  model using SDSS DR7 measurements of projected galaxy clustering, $\wprp (r_{\rm p})$ 
  of galaxies in $r$-band luminosity-threshold samples. 
  The decorated HOD is a model for the galaxy--halo
  connection that augments the traditional HOD by allowing for the possibility of 
  {\em galaxy assembly bias}: galaxy luminosity may be correlated with dark matter halo
  properties besides mass, $\mvir$. We demonstrate that it
  is not possible to rule out galaxy assembly bias using DR7 measurements of galaxy 
  clustering alone. Moreover, galaxy samples $\magr<-20, -20.5$
  favor strong levels of central galaxy assembly bias. These samples prefer scenarios  
  in which high-concentration halos are more likely to host a central galaxy
  relative to low-concentration halos of the same $\mvir.$ We rule out
  zero assembly bias with high significance for these
  samples. Satellite galaxy assembly bias is significant for the
  faintest sample we study, $\magr<-19.$ We find no evidence for
  assembly bias in the $\magr<-21$ sample. Assembly bias should be accounted for 
  in galaxy clustering analyses or attempts to exploit galaxy clustering to constrain cosmology. 
  In addition to presenting the first constraints on HOD models that accommodate assembly bias, our analysis 
  includes numerous improvements over previous analyses of this data set and 
  supersedes previously published results, even in the case of a standard HOD analysis.
\end{abstract}

@@

In much of the literature on this topic,
the character of the supporting evidence
suffers from a severe shortcoming.
Until very recently, the only models that have been fit to
observational clustering measurements have been traditional models
in which assembly bias is assumed from the outset to be zero.
Models that include assembly bias such as semi-analytic models
are typically too computationally expensive to compare to data in a manner 
that enables statistical constraints on model parameters 
\citep[but see][for recent progress in this direction]{lu_etal11,lu_etal12,henriques_etal13,lu_etal14}. 
Such models are usually 
compared to data on a case-by-case basis \citep[e.g.,][]{croton_etal07}, prohibiting
any conclusive statement to be made about the strength of any assembly bias signal.

@@

We use publicly available\footnote{\tt http://www.slac.stanford.edu/$\sim$behroozi/BPlanck\_Hlists} dark matter
halo catalogs based on the {\tt ROCKSTAR} halo-finder \citep{behroozi_rockstar11} 
and {\tt CONSISTENT TREES} algorithm \citep{behroozi_trees13}. In particular, we use the {\tt halotools\_alpha\_version2} 
version of the $z=0$ snapshot
of the {\tt `bolplanck'} catalog included with {\tt Halotools.} Halos in these catalogs are defined by the virial 
radius density contrast given in \citet{bryan_norman98} and have virial masses $\mvir$ within their virial 
radii. When populating this catalog with mock galaxies, we only use
present-day host halos with a value of $M_{\rm peak}$ that exceeds $300$ particles, where $M_{\rm peak}$ is 
the maximum mass a halo obtains during its evolution. We consider only host halos and not their 
subhalos in this work. For host halos, $M_{\rm peak}$ is almost always nearly identical to the 
present day virial mass of the halo, $\mvir$. The minimum 
peak halo mass considered in our analysis has $M_{\rm peak} \ge 4.05 \times 10^{10}\, h^{-1}\mathrm{M}_{\odot}$ 
and this prevents us from analyzing samples with $M_r > -19$. Throughout the remainder of this 
paper, we will refer only to the virial mass $\mvir$ of the halo to be in closer concordance with other 
work on HOD analyses.

@@

The five parameters of HOD models that are varied in standard analyses are $\log (M_{\rm min})$,
$\sigma_{\log M}$, $\alpha$, $\log (M_1)$, and $\log (M_0)$, though, as we show below, central galaxies usually
outnumber satellite galaxies by a factor of several, so $\log (M_{\rm min})$ and $\sigma_{\log M}$ usually
vary along a narrow degeneracy that fixes the total galaxy number density to the observed value. There are
many particular choices that can be made for the functional forms of $\langle N_{\rm cen}\vert \mvir \rangle$ and
$\langle N_{\rm sat}\vert \mvir \rangle$. We have made choices that mimic the standard SDSS DR7 analysis of
\citet{zehavi_etal11}, to expedite comparisons with their results. However, our choice does deviate from 
\citet{zehavi_etal11} in one respect. The mean satellite occupation of \citet{zehavi_etal11} 
is that of Eq.~(\ref{eq:nsat}) multiplied by an overall factor of $\langle N_{\rm cen} \vert \mvir \rangle$. 
We have chosen not to use this as our default because it can introduce difficulties in some analyses 
\citep[see the discussion of blue galaxy samples in][]{zentner_etal14} and because, as we have verified 
explicitly, the extra factor introduces only small quantitative changes to our results and no qualitative 
changes.

@@

After populating a halo catalog with mock galaxies, we calculate the
comoving number density of our mock galaxy sample as $n_{\rm g} =
N_{\rm gal} / L_{\rm box}^3$, where $N_{\rm gal}$ is the total number of
galaxies in the mock sample. We apply the distant-observer
approximation and use the simulation $z$-axis as the line-of-sight
direction, and the distance between points in the $xy$-plane to define
the projected distance $\rp.$ We place mock galaxies into
redshift-space by replacing each galaxy's $z$-coordinate with
$z_{\rm RS} = z + V_{\rm z}/H_0$\footnote{A similar exercise is demonstrated 
as part of the Halotools documentation at {\tt http://halotools.readthedocs.io}}. 
Having populated mocks, 
we perform the computation of the projected two-point galaxy correlation 
function, $w_{\rm p}(r_{\rm p})$ using the publicly-available {\tt CorrFunc} 
package \citep{corrfunc} which has been extensively optimized for computational speed.
We count pairs of points in each of
our $\rp$ bins, rejecting pairs with line-of-sight distances in redshift space, $\Delta z_{\rm RS}$, 
exceeding $\pi_{\rm max}=60$ ${\rm Mpc/h}$, which is the same projection
depth chosen by \citet{zehavi_etal11}, both in their analysis of the SDSS
DR7 data and in their modeling.

@@

%=-------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=8.0cm]{central_hod_comparison.pdf}
\includegraphics[width=8.5cm]{satellite_hod_comparison.pdf}
\caption{
The first moments of the central (left panel) and satellite (right) 
occupation distributions from the best-fit models to the 
$\magr \le -20$ sample. The solid, purple curve shows the HOD of our best-fit model
that includes the effect of assembly bias; the solid, orange curve shows the HOD
of the best-fit model in which assembly bias is assumed to be zero;
the dashed, black curve shows the best-fit HODs from \citet{zehavi_etal11}.
The light purple error band around the decorated HOD results contains 68\% of 
all samples of the posterior within $\Delta \chi^2 \le 5.89$ of the best-fit model at 
each bin of halo mass. For any individual model, 
the values of the HOD at each mass point are obviously correlated and do 
not vary independently from one mass bin to another. 
}
\label{fig:directhodcomparison}
\end{center}
\end{figure*}
%----------------------------------------------------------------------------------------------------

@@

Though the evidence for assembly bias is the most significant for the $M_r<-20$ sample,
there are hints of galaxy assembly bias in other samples. Satellite galaxies show a marginal preference
for occupying halos of higher concentration in the $M_r < -19$ threshold sample, with $A_{\rm sat}>0$ at 
85\%. The $M_r < -19.5$ sample exhibits weak preference for a positive correlation of galaxy occupation 
with halo concentration at fixed mass for both satellite galaxies and central galaxies. The low value of 
$\chi^2$ in this case is also suggestive of possible over-fitting using these additional parameters (but see 
the discussion in the subsequent paragraph). Continuing upward with luminosity,
the $M_r < -20.5$ sample exhibits a significant preference for central galaxy assembly bias, 
with $A_{\rm cen}>0$ at 92.3\%. Lastly, there is no preference for either central galaxy or 
satellite galaxy assembly bias for the $M_r < -21$ threshold sample, 
for which both $A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$
are consistent with zero well within 1$\sigma$. While we give a brief discussion of these results 
in the following section, the implications of all of these results, particularly for 
quantities derived from HODs, are far too numerous 
to address comprehensively in the present manuscript; 
however, we plan to address them in forthcoming publications.

@@

Another possible explanation for having more luminous galaxies reside
in higher concentration halos is halo-halo interactions.  Recent work
on halo evolution suggests that a more physical definition of the size
of a halo should be $\sim 2-3$ times the traditional virial radius
\citep{wetzel_etal14,adhikari_etal14,wetzel_nagai15,more_etal15,sunayama_etal16}.
This ``splashback radius" incorporates ``splashback" halos that have
passed within the dense environment of the central halo, but are
traditionally classified as distinct halos despite being strongly
influenced by the environment of the central
halo. \citet{wang_etal09}, \citet{wetzel_etal14}, and 
\citet{sunayama_etal16}, all find that these ``splashback" halos are a
significant cause of halo assembly bias on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, where assembly bias is most pronounced and
strongly scale dependent. Consequently, decorated HOD models exhibit
this same feature \citep{hearin_etal16}, and is not a coincidence that
the greatest improvement of the decorated HOD in the description of
galaxy clustering occurs on these same length scales (see
Fig.~\ref{fig:Mr19samples}-\ref{fig:Mr21samples} and the associated
discussion).

This ``splashback" hypothesis has further merit in that it has the
same sense as suggested by the data. Splashback halos have experienced
mass loss as a consequence of their tidal interactions with a larger,
nearby halo. As a consequence, splashback halos are expected to be
less massive than `regular' host halos that host similar galaxies
\citep{dalal_etal08}.  Meanwhile, high concentrations 
are a hallmark of splashback halos
\citep{sunayama_etal16}. The implication is
a population of halos, correlated on scales $r \sim 1-3\,
h^{-1}\mathrm{Mpc}$, that have concentrations that are high for their
mass and galaxies that are overluminous for their mass. This is
precisely the sense of assembly bias suggested by our analysis.  Note,
though, that this splashback effect cannot explain galaxy assembly
bias on large, linear scales.

@@

We have re-analyzed the SDSS DR7 measurements of projected galaxy clustering,
$\wprp,$ and number density, $n_{\rm g},$ originally published in \citet{zehavi_etal11}.
The novelty of our work is that we have performed these analyses using the
decorated Halo Occupation Distribution (HOD) formalism, which allows for galaxy
assembly bias and was introduced by \citet{hearin_etal16} precisely for this purpose.
In this work, we provide the first quantitative constraints on
assembly bias derived from the Decorated HOD. Projected galaxy clustering, 
$\wprp(r_{\rm p})$ is already very well-measured within SDSS DR7, therefore it is likely 
that further improvements on assembly bias constraints at low-redshift will require the use of additional 
observables such as galaxy--galaxy lensing, group statistics, void statistics, or numerous other possibilities. 
We are currently exploring many of those possibilities and will report on those results in forthcoming publications.

Our most important conclusions are as follows.
%
\ben
%
\item It is not possible to rule out galaxy assembly bias using SDSS DR7 measurements of $\wprp$ and $n_{\rm g}.$
%
\item Decorated HOD fits to $\wprp$ and $n_{\rm g}$ favor significant levels of assembly bias, particularly in the lower luminosity thresholds we study. Both the $\magr<-20, -20.5$ samples prefer relatively strong central galaxy assembly bias. The $\magr<-19$ sample favors satellite assembly bias. Assembly bias in these samples improves the capability of the model to describe galaxy clustering near
the one-halo to two-halo transition at $r_{\rm p} \sim 2 \, h^{-1}\mathrm{Mpc}$.
%
\item The evidence for galaxy assembly bias weakens for brighter galaxy samples: 
Decorated HOD fits to the $\magr<-21$ sample are consistent with both $A_{\rm cen}=0$ and $A_{\rm sats}=0.$ 
This is consistent with the well-established result that
{\em halo assembly bias} weakens with increasing halo mass over the dynamic range relevant to these galaxy samples
\citep[see, e.g., Figure 8 of][and references therein]{hearin_etal16}.
%
\item Our posteriors and best-fit parameters summarized in
Table \ref{table:parameters} supersede the values published in \citet{zehavi_etal11},
as direct-mock-population together with the Decorated HOD allows us to account for
highly significant systematics that have heretofore been neglected from all HOD fits to SDSS data.
We note that our findings update the original \citet{zehavi_etal11} results
{\em even for our fits to standard HODs without assembly bias}, because
the original results were derived from MCMC chains that did not sufficiently sample the HOD model posteriors.
%
\een
%

@@

We thank Zheng Zheng for his help in diagnosing the
differences between the present analysis and the SDSS DR7
analysis presented in \citet{zehavi_etal11}. We thank Manodeep 
Sinha for help installing and running the {\tt CorrFunc} package 
as well as comments on an earlier draft of this manuscript. ARZ and 
APH are grateful to Prince Rogers Nelson for inspiring our creativity. 
The authors gratefully acknowledge the Gauss Centre for Supercomputing
e.V. (www.gauss-centre.eu) and the Partnership for Advanced
Supercomputing in Europe (PRACE, www.prace-ri.eu) for funding the
MultiDark simulation project by providing computing time on the GCS
Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ,
www.lrz.de). The Bolshoi simulations have been performed within the
Bolshoi project of the University of California High-Performance
AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
Research Center. The work of ARZ was supported by the US National Science
Foundation via grant AST 1517563. FvdB and JUL are supported by the US National Science
Foundation through grant AST 1516962. APH is funded through the Yale Center 
for Astronomy \& Astrophysics Prize fellowship.
